Comparing OTU quality across clustering strategies

### 2021-07-16 exploratory/2021/algorithm_diagram.Rmd
May try using reticulate
Specify python path
correct conf mat

```{r lib}
library(tidyverse)
library(diagram)
```

@@

# Pat's method for plotting the network graph
# last example from OptiClust supplemental text
tp <- 12
tn <- 1210
fp <- 0
fn <- 3
names <- c(	"B,D,I", "E,F,Q", "C,G", "A,H,J", "M,N", "L,O,P", "K", "...")
n_seqs <- length(names)
M <- matrix(nrow = n_seqs, ncol = n_seqs, byrow = TRUE, data = 0)
rownames(M) <- colnames(M) <- names
C <- matrix(nrow = n_seqs, ncol = n_seqs, byrow = TRUE, data = 0)
rownames(C) <- colnames(C) <- names

@@

@@

>>>>

```{r lib}
library(tidyverse)
library(diagram)
library(reticulate)
use_python('~/miniconda3/bin/python')
```

@@

# Pat's method for plotting the network graph
# last example from OptiClust supplemental text
tp <- 14
tn <- 1210
fp <- 0
fn <- 1
names <- c(	"B,D,I", "E,F,Q", "C,G", "A,H,J", "M,N", "L,O,P", "K", "...")
n_seqs <- length(names)
M <- matrix(nrow = n_seqs, ncol = n_seqs, byrow = TRUE, data = 0)
rownames(M) <- colnames(M) <- names
C <- matrix(nrow = n_seqs, ncol = n_seqs, byrow = TRUE, data = 0)
rownames(C) <- colnames(C) <- names

@@

## plot several optifit iterations

@@

## maybe I'll do everything before plotting in python

#```{python}
#r.g1
#```
